Trends from 30-Year Observations of Downward Solar Irradiance in Thessaloniki, Greece

### 2024-09-13 MDPI_submission.Rmd
Commit 2024-09-13 10:14

We have analyzed a 30-year dataset of SRD measurements in Thessaloniki, Greece 
(`r paste(year(min(ALL_1_daily_DESEAS$Date)), " -- ", year(max(ALL_1_daily_DESEAS$Date)))`), aiming to identify the long-term 
variability of solar irradiance under different sky conditions.
Under all-sky conditions, there is a positive trend in SDR of 
$`r alltrend`\,\%/y$ (brightening). 
A previous study [@Bais2013] for the period 1993--2011 also reported a
positive trend of $0.33\,\%/y$.
The slight increase in this trend indicates that the brightening of SDR
continues and is likely caused by continuing decreases in aerosol optical
depth and the optical thickness of clouds over the area.
A smaller trend has been found under clear-sky conditions
($`r cleartrend`\,\%/y$), which supports the notion that part of the
brightening is caused by decreasing aerosols.
@Siomos2020 showed that aerosol optical depth over Thessaloniki
was decreasing constantly, at least up until 2018.
The attenuation of SDR by aerosols over Europe has been proposed as
major factor by @Wild2021.
Unfortunately, for this study, aerosol data for the entire period were
not available in order to quantify their effect on SDR. 
The brightening effect on SDR under cloudy-sky conditions
($`r cloudtrend`\,\%/y$) suggests that cloud optical thickness 
is also decreasing during this period.
As long-term data of cloud optical thickness are
also not available for the region, we cannot draw quantitative
conclusions.

>>>>

We have analyzed a 30-year dataset of SDR measurements in Thessaloniki, Greece 
(`r paste(year(min(ALL_1_daily_DESEAS$Date)), " -- ", year(max(ALL_1_daily_DESEAS$Date)))`), aiming to identify the long-term 
variability of solar irradiance under different sky conditions.
Under all-sky conditions, there is a positive trend in SDR of 
$`r alltrend`\,\%/y$ (brightening). 
A previous study [@Bais2013] for the period 1993--2011 also reported a
positive trend of $0.33\,\%/y$.
The slight increase in this trend indicates that the brightening of SDR
continues and is likely caused by continuing decreases in aerosol optical
depth and the optical thickness of clouds over the area.
A smaller trend has been found under clear-sky conditions
($`r cleartrend`\,\%/y$), which supports the notion that part of the
brightening is caused by decreasing aerosols.
@Siomos2020 showed that aerosol optical depth over Thessaloniki
was decreasing constantly, at least up until 2018.
The attenuation of SDR by aerosols over Europe has been proposed as
major factor by @Wild2021.
Unfortunately, for this study, aerosol data for the entire period were
not available in order to quantify their effect on SDR. 
The brightening effect on SDR under cloudy-sky conditions
($`r cloudtrend`\,\%/y$) suggests that cloud optical thickness 
is also decreasing during this period.
As long-term data of cloud optical thickness are
also not available for the region, we cannot draw quantitative
conclusions.
